Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-18 article.tex
comment modified

% Discussion about the metrics Observing Tab.\ref{tab:tab1}, it appears that
best methods only infer the \textbf{undirected} network by giving the same
weights to both edges $(i,j)$ and $(j,i)$. This is quite surprising
considering the goal of the challenge, namely predicted directed connections
between neurons. Besides, if the true network undirected, i.e. for all links
$(i,j)$, back links are added, is the infered network then the score obtained
according to the ROC AUC metric is very high ($\sim 0.9956$ on
\textit{normal-1}). Therefore, an undirected infered network seems sufficient
to maximize the ROC AUC score without trying to identify the link direction.
Indeed, predicting perfectly directivity only yields a small gain ($\sim
0.005$ on \textit{normal-1}) which is is not very rewarding. In contrast, the
same experiment with the precision recall metric rewards less the undirected
network and the gain margin in predicting the link directivity is large enough
to be interesting. For these reason, it seems that the metric used in the
contest, i.e. the ROC AUC, does not seem consistent with the goal of
predicting directed connections between neurons. Another metric, such as the
AUC PRC, is maybe more appropriate to assess the quality of the
\textbf{directed} infered network.

Interestingly, an easy way to improve results for asymmetric method (see Tab.\ref{tab:tab2}), namely GTE and GENIE3, is to make undirected the infered network.

>>>>

%% Depth -- Gilles chapitre 7

% Discussion about the metrics

Observing Tab.\ref{tab:tab1}, it appears that
best methods only infer the \textbf{undirected} network by giving the same
weights to both edges $(i,j)$ and $(j,i)$. This is quite surprising
considering the goal of the challenge, namely predicted directed connections
between neurons. Besides, if the true network undirected, i.e. for all links
$(i,j)$, back links are added, is the infered network then the score obtained
according to the ROC AUC metric is very high ($\sim 0.9956$ on
\textit{normal-1}). Therefore, an undirected infered network seems sufficient
to maximize the ROC AUC score without trying to identify the link direction.
Indeed, predicting perfectly directivity only yields a small gain ($\sim
0.005$ on \textit{normal-1}) which is is not very rewarding. In contrast, the
same experiment with the precision recall metric rewards less the undirected
network and the gain margin in predicting the link directivity is large enough
to be interesting. For these reason, it seems that the metric used in the
contest, i.e. the ROC AUC, does not seem consistent with the goal of
predicting directed connections between neurons. Another metric, such as the
AUC PRC, is maybe more appropriate to assess the quality of the
\textbf{directed} infered network.

Interestingly, an easy way to improve results for asymmetric method (see
Tab.\ref{tab:tab2}), namely GTE and GENIE3, is to make undirected the infered
network. It proves once again that trying to detect the link direction is more
penalizing than rewarding.
